|

### 2020-05-20 nontex/install/git/fs_git_setup.Rmd
8 pane timeline text and panes fully parametrized and dynamically sized.

>>>>

## Versioning and Tagging

[Git Tagging](https://git-scm.com/book/en/v2/Git-Basics-Tagging). [Semantic Versioning](https://semver.org/):

Given a version number MAJOR.MINOR.PATCH, increment the:

1. MAJOR version when you make incompatible API changes,
2. MINOR version when you add functionality in a backwards compatible manner, and
3. PATCH version when you make backwards compatible bug fixes.

Additional labels for pre-release and build metadata are available as extensions to the MAJOR.MINOR.PATCH format.

By default, the **git push** command doesn’t transfer tags to remote servers. You will have to explicitly push tags to a shared server after you have created them. This process is just like sharing remote branches — you can run git push origin <tagname>.

```{bash}
git tag -l
git tag -a v0.1.1 -m "Genereate Package after updating to R 4.0.0 Arbor Day."
git show v0.1.1
git push github v0.1.1
```

## Githug pages

local test github pages. [Testing your GitHub Pages site locally with Jekyll](https://help.github.com/en/github/working-with-github-pages/testing-your-github-pages-site-locally-with-jekyll).

For testing github pages sites. On windows, install ruby using [windows-installer](https://rubyinstaller.org/downloads/). Windows choose install option 3, install toolchain.

[jekyll with bundler](https://jekyllrb.com/tutorials/using-jekyll-with-bundler/)

```{bash}
ruby -v
gem -v 
gcc -v
g++ -v 
make -v

gem install jekyll bundler
jekyll -v
gem install bundler
gem install minima
gem install jekyll-feed

cd ~/fanwangecon.github.io
<!-- delete existing Gemfile Gemfile.lock possibly in directory -->
bundle init
bundle config set --local path 'vendor/bundle'
bundle add jekyll
bundle add minima
bundle add jekyll-feed
bundle exec jekyll new --force --skip-bundle .

bundle exec jekyll serve
http://localhost:4000

https://jekyllrb.com/tutorials/using-jekyll-with-bundler/
```

### 2020-05-20 nontex/install/windows/fn_installations.Rmd
8 pane timeline text and panes fully parametrized and dynamically sized.

@@

```{bash}
cd ~/pyfan
cd "C:/Users/fan/pyfan"
poetry install
make html
rm -rf dist/ build/
poetry build
poetry publish
```

@@

```{bash}
pip show pyfan
# conda activate pyfan
pip install pyfan
```

##### Uninstall

@@

@@

```{r}
# Can enter R from Command Prompt Conda ENV, much faster than from r-studio
# Install R-tools, RTOOLS is for WINDOWS
install.packages("installr")
library("installr")
install.Rtools()
# c:/Rtools/bin;
# c:/Rtools/mingw_32/bin;
# c:/Rtools/mingw_64/bin;

# main packagevps
# tidymodel installation on linux difficult
install.packages(c("tidyverse", "tidymodels", "tidyr"))
# development packages
install.packages(c("devtools", "IRkernel", "pkgdown", "roxygen2", "kableExtra"))
# other packages
install.packages(c("AER", "minpack.lm", "knitr", "matlab"))

@@

>>>>

Theme for sphinx
```{bash}
pip install sphinx-rtd-theme
pip install sphinx_bootstrap_theme
```

@@

[sphinx readthedocx](https://samnicholls.net/2016/06/15/how-to-sphinx-readthedocs/)

```{bash}
cd ~/pyfan
cd "C:/Users/fan/pyfan"
poetry install

rm -rf dist/ build/ docs/
cd docs/
sphinx-build -b html ../ _build
<!-- make html -->
sphinx-build -b latexpdf ../ _build
make latexpdf

poetry build
poetry publish
```

@@

```{bash}
pip show pyfan
# conda activate pyfan
pip install pyfan
pip install git+https://github.com/fanwangecon/pyfan.git#egg=pyfan
```

```{bash}
ipython
import pyfan.util.rmd.bookdownparse as bookdownparse
?bookdownparse.fs_yml2readme
```
##### Uninstall

@@

#### Conda Jekyll Environment (Ruby)

For testing github pages sites. On windows, install ruby using [windows-installer](https://rubyinstaller.org/downloads/). Windows choose install option 3, install toolchain.

```{r}
# Set up
conda deactivate
conda list env
conda env remove -n wk_ruby
conda create -n wk_ruby -y
conda activate wk_ruby

ruby -v
gem -v 
gcc -v
g++ -v 
make -v

gem install jekyll bundler

@@

```{r}
# Install RTools First!
# https://cran.r-project.org/bin/windows/Rtools/

# Install tidyverse
install.packages(c("tidyverse", "tidymodels"))

# Install Packaging tools
install.packages(c("devtools", "pkgdown", "roxygen2", "bookdown", "knitr", "kableExtra", "formatR"))

# Install Statistics models
install.packages(c("AER", "minpack.lm"))

# Install Tools to Work with Other Packages
install.packages(c("reticulate"))

# Personal Packages
devtools::install_github("fanwangecon/REconTools")
```
```{r}
# Can enter R from Command Prompt Conda ENV, much faster than from r-studio
# Install R-tools, RTOOLS is for WINDOWS
# install.packages("installr")
# library("installr")
# install.Rtools()
# c:/Rtools/bin;
# c:/Rtools/mingw_32/bin;
# c:/Rtools/mingw_64/bin;

# Install RTools First!
https://cran.r-project.org/bin/windows/Rtools/

# main packagevps
# tidymodel installation on linux difficult
# install.packages(c("tidyverse", "tidymodels", "tidyr"))
# development packages
# install.packages(c("devtools", "IRkernel", "pkgdown", "roxygen2", "kableExtra"))
# other packages
install.packages(c("AER", "minpack.lm"))
# install.packages(c("AER", "minpack.lm", "knitr", "matlab"))

# for working with other tools
# install.packages(c("reticulate"))

@@

# Present
install.packages("revealjs")
# Kernel
# install.packages(c('repr', 'IRdisplay', 'evaluate', 'crayon', 'pbdZMQ', 'devtools', 'uuid', 'digest'))
# IRkernel::installspec()
```
